``Dr.~Tustison (UVA) presentation''

### 2016-08-04 ants2015build.Rmd
ENH:  More.

![](./figures/shape_appearance.png)
-->

@@

--------------------------------------------------------------------------------------
Script by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
```

@@

* "*Let's incorporate N3 into ANTs!*"
-->

## N3 adoption issues

@@

@@

![](./tools/atropos/figures/atroposFlow.png)
-->

@@

## So how does ATITH compare with ANTs, FS?

@@

>>>>

![](./figures/shape_appearance.png)

@@

--------------------------------------------------------------------------------------
script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
multivariate template adaption by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
```

-->

@@

* "*Let's incorporate N3 into ANTs!*"

@@

-->

![](./tools/atropos/figures/atroposFlow.png)

## ```DenoiseImage``` --- contribution from Jose Manjon

![](./tools/figures/denoising.png)

```bash
$ DenoiseImage --help

     -n, --noise-model Rician/(Gaussian)
          Employ a Rician or Gaussian noise model.

     -x, --mask-image maskImageFilename
          If a mask image is specified, denoising is only performed in the mask region.

     -p, --patch-radius 1
                        1x1x1
          Patch radius. Default = 1x1x1

     -r, --search-radius 3
                         3x3x3
          Search radius. Default = 3x3x3.

     --help
          Print the help menu.
          <VALUES>: 1

```

* ``Correct'' images

    * motion correction

    * ``remove'' lesions

* Project atlas set intensity signature

* Use in ``corrective learning''

@@

## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)

```bash
$ antsJointFusion --help

COMMAND:
     antsJointFusion
          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
          original label fusion framework was extended to accommodate intensities by Brian
          Avants. This implementation is based on Paul's original ITK-style implementation
          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
          with joint label fusion and corrective learning--an open source implementation,
          Front. Neuroinform., 2013.

     -t, --target-image targetImage
                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
          The target image (or multimodal target images) assumed to be aligned to a common
          image domain.

     -g, --atlas-image atlasImage
                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
          The atlas image (or multimodal atlas images) assumed to be aligned to a common
          image domain.

     -l, --atlas-segmentation atlasSegmentation
          The atlas segmentation images. For performing label fusion the number of
          specified segmentations should be identical to the number of atlas image sets.

     -a, --alpha 0.1
          Regularization term added to matrix Mx for calculating the inverse. Default =
          0.1

     -b, --beta 2.0
          Exponent for mapping intensity difference to the joint error. Default = 2.0

     -r, --retain-label-posterior-images (0)/1
          Retain label posterior probability images. Requires atlas segmentations to be
          specified. Default = false

     -f, --retain-atlas-voting-images (0)/1
          Retain atlas voting images. Default = false

     -c, --constrain-nonnegative (0)/1
          Constrain solution to non-negative weights.

     -p, --patch-radius 2
                        2x2x2
          Patch radius for similarity measures. Default = 2x2x2

     -m, --patch-metric (PC)/MSQ
          Metric to be used in determining the most similar neighborhood patch. Options
          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
          correlation).

     -s, --search-radius 3
                         3x3x3
                         searchRadiusMap.nii.gz
          Search radius for similarity measures. Default = 3x3x3. One can also specify an
          image where the value at the voxel specifies the isotropic search radius at that
          voxel.

     -e, --exclusion-image label[exclusionImage]
          Specify an exclusion region for the given label.

     -x, --mask-image maskImageFilename
          If a mask image is specified, fusion is only performed in the mask region.

     -o, --output labelFusionImage
                  intensityFusionImageFileNameFormat
                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
          The output is the intensity and/or label fusion image. Additional optional
          outputs include the label posterior probability images and the atlas voting
          weight images.

     --version
          Get version information.

     --help
          Print the help menu.
          <VALUES>: 1

```

-->

@@

-->

<!--
----

_So how does ATITH compare with ANTs, FS?_

@@

----

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)

-->

### 2016-08-04 evaluation/antsvfreesurfer2.Rmd
ENH:  Final commit.
ENH:  More.

<!--
* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
* Acquisition and anonymization (e.g. defacing) protocols are often different.
-->

@@

<!--
Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
to produce auxiliary images which are used for brain extraction and brain segmentation.
-->

@@

Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-->

@@

Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
-->

@@

* Public data sets (IXI, NKI, OASIS, MMRR)
* $>$ 1200 subjects, age 4 to over 94 years old
-->

>>>>

* Templates representing the average mean shape and intensity are built directly from the
* cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
* Acquisition and anonymization (e.g. defacing) protocols are often different.

@@

Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
to produce auxiliary images which are used for brain extraction and brain segmentation.

@@

Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)

@@

Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.

@@

* Public data sets (IXI, NKI, OASIS, MMRR)
* $>$ 1200 subjects, age 4 to over 94 years old

### 2016-08-04 ibm.Rmd
ENH:  More.

<!--
##  Founders:  Brian and Nick
-->

@@

<!--
$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-->

@@

<!--
# Competitions
-->

@@

@@

<!--
## Nonparametric nonuniform intensity normalization (N3)

@@

<!--
```bash
$ DenoiseImage --help

@@

```
-->

>>>>

##  Founders:  Brian and Nick

@@

$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...

@@

# ANTs lineage

## Image mapping and perception: 1877

Francis Galton: _Can we see criminality in the face?_

![](./figures/galton.png)

_What about syphilis, mental illness?_

<!--
Notes:
* Use of "composite portraiture" and what he called "eugenics"
* Can we see criminality, mental illness, syphilis, and others in facial features?
* Despite the obvious prejudices driving his research, he was a pioneer.
-->

@@

##

![](./background/figures/FrancisGalton2.jpg)
-->

<!--
Notes:
* Another example where he has manually categorized facial features and try to combine them
* Did not find much---composite tends to blend away to normality.
-->

##  Speaking of criminality...

_Can we say anything about the U.S. Congress?_

![](./background/figures/congressPersons.png)

__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__

<!--
Notes:
-->

##  Image mapping & biology:  1917

D'Arcy Thompson: _Comparison of related forms_

![](./figures/dthompson.png)
-->

<!--
Notes:
* Book: On Growth and Form
* Descriptive
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

## Image mapping & biology: Current
<BR><BR>
_Look where we are now!_
<BR><BR>
![](./background/figures/r16xr85.png)

<!--
## ANTs family tree

![](./figures/lineage.jpg)
-->

<!--
References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-->

<!--
## Initial scope

![](./figures/ants_initial_scope.png)
-->

<!--
Notes:
* Brian work with Murray Grossman
* First registration paper
  - WBIR submission
  - FEM registraiton using B-spline basis functions.
  - "yeah, that registration is not that good---Jim would not like it."
-->

# Competitions

@@

@@

```bash
$ DenoiseImage --help

@@

### 2016-08-04 ibm.tex
ENH:  More.

@@

@@

@@

\begin{frame}{Gender discernibility?}

@@

\begin{frame}{N3 adoption issues}

@@

@@

\begin{frame}{\texttt{DenoiseImage} --- contribution from Jose Manjon}

@@

@@

@@

@@

@@

\section{But, wait, there's more!}\label{but-wait-theres-more}

\begin{frame}{ANTs tools are multivariate}

\includegraphics{./evaluation/figures/rfRmse05ANTsT1T2.png}

\begin{frame}{Longitudinal processing}

\includegraphics{./longitudinal/figures/longitudinalPipeline.png}

>>>>

\begin{frame}{``Free beer''}

\includegraphics{./licenses/figures/freebeerfreespeech.jpg}

@@

\section{ANTs lineage}\label{ants-lineage}

\begin{frame}{Image mapping and perception: 1877}

Francis Galton: \emph{Can we see criminality in the face?}

\includegraphics{./figures/galton.png}

\emph{What about syphilis, mental illness?}

\begin{frame}{Speaking of criminality\ldots{}}

\emph{Can we say anything about the U.S. Congress?}

\includegraphics{./background/figures/congressPersons.png}

\textbf{Maybe they should have used
\href{https://github.com/ntustison/CongressionalFaceTemplates}{ANTs}?}

\begin{frame}{Image mapping \& biology: 1917}

D'Arcy Thompson: \emph{Comparison of related forms}

\includegraphics{./figures/dthompson.png} --\textgreater{}

\begin{frame}{Image mapping \& biology: Current}

 \emph{Look where we are now!}
\includegraphics{./background/figures/r16xr85.png}

\section{Competitions}\label{competitions}

\begin{frame}{Algorithmic fight club}

\includegraphics{./competitions/figures/fightclub.jpg}

@@

\begin{frame}{Neuro tools}

\includegraphics{./tools/figures/coreANtsToolsNeuro.png}

\begin{frame}{Pulmonary tools}

\includegraphics{./tools/figures/coreANtsToolsLung.png}

\begin{frame}{Symmetric Normalization (SyN)}

\(\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2\)

\includegraphics{./papers/figures/fishes.png}

--\textgreater{}

NOtes: * Previously discussed Brians work * The variant most widely used
--\textgreater{}

\begin{frame}{Diffeomoprhisms: differentiable map with diff. inverse}

\includegraphics{./figures/highresdiffeos.jpg}

\begin{frame}{Diffeomorphisms: image parameterization in a metric space}

\includegraphics{./figures/shape_appearance.png}

@@

\begin{frame}{Gender?}

@@

@@

\begin{frame}[fragile]{N4 (``Nick's N3'')}

\begin{itemize}
\item
  comparative
  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
\item
  small spline distances (useful for higher magnet strengths)
\item
  multiresolution
\item
  weighted regional mask (used in
  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
\item
  fast execution times
\item
  \emph{publicly available}
\item
  tested nightly within the ITK dashboard system
\end{itemize}

@@

\begin{frame}[fragile]{\texttt{DenoiseImage} --- contribution from Jose
Manjon}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{DenoiseImage} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{DenoiseImage}
          \KeywordTok{Denoise} \NormalTok{an image using a spatially adaptive filter originally described in J. V.}
          \KeywordTok{Manjon}\NormalTok{, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive}
          \KeywordTok{Non-Local} \NormalTok{Means Denoising of MR Images With Spatially Varying Noise Levels,}
          \KeywordTok{Journal} \NormalTok{of Magnetic Resonance Imaging, 31:192-203, June 2010.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
          \KeywordTok{image.}

     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
          \KeywordTok{A} \NormalTok{scalar image is expected as input for noise correction.}

     \KeywordTok{-n}\NormalTok{, --noise-model Rician/(Gaussian)}
          \KeywordTok{Employ} \NormalTok{a Rician or Gaussian noise model.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{If} \NormalTok{a mask image is specified, denoising is only performed in the mask region.}

     \KeywordTok{-s}\NormalTok{, --shrink-factor (1)}\KeywordTok{/2/3/...}
          \KeywordTok{Running} \NormalTok{noise correction on large images can be time consuming. To lessen}
          \KeywordTok{computation} \NormalTok{time, the input image can be resampled. The shrink factor, specified}
          \KeywordTok{as} \NormalTok{a single integer, describes this resampling. Shrink factor = 1 is the}
          \KeywordTok{default.}

     \KeywordTok{-p}\NormalTok{, --patch-radius 1}
                        \KeywordTok{1x1x1}
          \KeywordTok{Patch} \NormalTok{radius. Default = 1x1x1}

     \KeywordTok{-r}\NormalTok{, --search-radius 3}
                         \KeywordTok{3x3x3}
          \KeywordTok{Search} \NormalTok{radius. Default = 3x3x3.}

     \KeywordTok{-o}\NormalTok{, --output correctedImage}
                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{noiseImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of the noise corrected version of the input image.}
          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated noise image.}

     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

@@

\begin{itemize}
\tightlist
\item
  Templates representing the average mean shape and intensity are built
  directly from the
\item
  cohort to be analyzed, e.g.~pediatric vs.~middle-aged brains.
\item
  Acquisition and anonymization (e.g.~defacing) protocols are often
  different.
\end{itemize}

@@

Each template is
\href{https://github.com/ntustison/antsCookTemplatePriorsExample}{processed}
to produce auxiliary images which are used for brain extraction and
brain segmentation.

\begin{frame}{Brain extraction comparison}

\includegraphics{./evaluation/figures/brainExtraction.png}

Comparison with de facto standard FreeSurfer package. Note the
difference in separation of the gray matter from the surrounding CSF. (0
failures out of 1205 scans)

\begin{frame}[fragile]{Brain segmentation}

\includegraphics{./evaluation/figures/brainSegmentation.png}

Randomly selected healthy individuals. \texttt{Atropos} gets good
performance across ages.

@@

\begin{frame}{Open science principles}

\includegraphics{./evaluation/figures/ageDistribution.png}

\begin{itemize}
\tightlist
\item
  Public data sets (IXI, NKI, OASIS, MMRR)
\item
  \(>\) 1200 subjects, age 4 to over 94 years old
\end{itemize}

@@
